marlin-paper-notes

### 2021-05-07 documents/marlin-paper-notes.Rmd
testing on ubuntu

>>>>

## optimization

similar SIR approach... why not just get it running first

Yields: sum of revenue of target species: or if you just say revenue, then you can manipulate prices to get desired impact: if you say that bycatch literally has no value then just set price to 0, or negative.

biodiversity: B/K of all species (for now): average or sum? Sum I think, since you'd rather have all at 0.5 than half at 0 and half at 1

yield_weight: do you have MSY for all species? I don't think so, and gets crazy complicated to think about MSY once you start messing with technical interactions etc. So you just need something to weight the marginal value of both.

So, for every step, you'll have N candidate cells, each with a marginal yield effect and a marginal biodiversity effect. You then need to rank each cell by the objective function. Need some function to convert yield and biomass into comparable units then. So just center and scale? alpha then controls the relative weight of a standard deviation increase in yield relative to a standard deviation increase in biodiversity? Issue there: once you're down to the last cell this won't work. Dividing by max caps both at 1, but no limit to the loss there... Rescale to be positive? yield - min(yield) + 1e-3 will ensure the min value is 1e-3, then scaling by max of that vector will make the max 1, so now everything has the same range. Oh, or just use scaes::rescale to put both on range of 0 to 1.

Is that going to have weird behavior rescaling at every iteration like that? i.e. the effective value of alpha will change depending on the scale of the biomass and yield. Setting alpha to 1 will maximize yields, setting it to 0 will maximize biodiversity, what does setting to 0.5 mean? value the best yield cell as much as the best biomass cell.

Seems good enough for now. So doing it this way, you only have to iterate over the weight, no different objective function shapes

So what are you optimizing? Location and size or just location? In theory, you can save some computation time by stopping the optimization when the objective function starts to consistently decline. But, since there might be multiplie maxima here, that could get tricky, and wouldn't allow you to look at tradeoff wedges. So...

- for each weight
- for each range of MPA sizes
- find the optimal MPA configuration. 
- Not too bad!

## what are you comparing optimization to

OK, you have some optimized results, so what. On the one hand, you can examine to what extent given this case study, tradeoffs across species or across yields are inevitable or just gotta find the right network.

From there though, can also compare "optimal" to "realistic"

Design strategies
1. Assign protection by SSB / SSB0 weighted abundance in space (protect the highest concentrations of the most threatened species)
2. Assign protection by bycatch rates (distribution of biomass bycatch / biomass target)
3. Assign protection by targeting fishing effort
4. Assign protection by avoiding fishing effort

Knowledge states
1. Degrees of accuracy over the thing being measured (i.e. error in the design strategy)

2. Number of species considered (e.g. design around only 2 bycatch species instead of all)

3. über naive: just close off random patches up to a specified size

We then plot these points in objective function space and compare to the efficiency frontier / consider frequency and magnitude of conservation and economic tradeoofs

The question all this is answering: how sensitive are conservation and economic outcomes to design strategy / uncertainty when there are technical interactions and heterogeneity in habitat? The first stage is teeing up the idea that beyond conservation / yield tradeoffs, as you increase habitat heterogeneity with technical interactions you increase the potential for conservation tradeoffs. But, the degree is going to be super context dependent, so to dive in a bit we then focus on this case study of the particular species / habitat overlap in the WCPO. Further work might reveal more generalities in this, but htis is basically getting a sense for the potential magnitude of the challenge.

OK, this is actually coming together! You should run the same design / knowledge states for the broader range of simulated habitats. That will make the point nice and clearly.

But, that begs the question of, is it an inevitable tradeoff, or just a case of poor design. That requires optimization. But, optimization is very computationally intensive. To examine this point then, we repeated the exercies, but with a specific case study where we hold habitat as constant, but redo the exercise conditional on constant habitat. We can then see to what extent tradeoofs persist, and ideally come up with some way of comparing the case study habitats to the metric of habitat heterogeneity in the full simulations. Case study also demonstrates that its a real thing: not making up the idea of different habitat use

This might actually be a cool paper. Proc B?
